\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{Tài liệu tham khảo}

\bibitem{requirements}
JobConnect repository, ``REQUIREMENTS.md -- Production MVP Recruiting Marketplace'', tài liệu yêu cầu sản phẩm nội bộ.

\bibitem{hld-overview}
JobConnect repository, ``Production HLD: Overview And Problem'', tài liệu kiến trúc mức cao.

\bibitem{hld-architecture}
JobConnect repository, ``Production HLD: Architecture Overview'', tài liệu kiến trúc backend.

\bibitem{hld-storage}
JobConnect repository, ``Production HLD: Data And Storage'', tài liệu thiết kế dữ liệu và lưu trữ.

\bibitem{hld-matching}
JobConnect repository, ``Production HLD: Matching And Search Pipeline'', tài liệu thiết kế matching và search.

\bibitem{hld-api}
JobConnect repository, ``Production HLD: API And Runtime Flows'', tài liệu luồng runtime và API.

\bibitem{hld-security}
JobConnect repository, ``Production HLD: Security, Notifications, And Audit'', tài liệu bảo mật, notification và audit.

\bibitem{lld-api}
JobConnect repository, ``Production LLD: API Contract'', tài liệu hợp đồng API production.

\bibitem{implementation-matrix}
JobConnect repository, ``Current API Implementation Matrix'', tài liệu đối chiếu hiện trạng triển khai với target contract.

\bibitem{greenhouse}
Greenhouse, ``Greenhouse platform'', \url{https://www.greenhouse.com/platform}.

\bibitem{lever}
Lever, ``LeverTRM ATS + CRM'', \url{https://www.lever.co/lever-trm}.

\bibitem{workday}
Workday, ``Workday Talent Acquisition'', \url{https://www.workday.com/en-us/products/talent-management/talent-acquisition.html}.

\bibitem{prf-bm25}
Stephen Robertson and Hugo Zaragoza, ``The Probabilistic Relevance Framework: BM25 and Beyond'', Foundations and Trends in Information Retrieval, 3(4):333--389, 2009. DOI: \url{https://doi.org/10.1561/1500000019}.

\bibitem{dpr}
Vladimir Karpukhin, Barlas Oğuz, Sewon Min, Patrick Lewis, Ledell Wu, Sergey Edunov, Danqi Chen, and Wen-tau Yih, ``Dense Passage Retrieval for Open-Domain Question Answering'', arXiv:2004.04906, 2020. \url{https://arxiv.org/abs/2004.04906}.

\bibitem{sbert}
Nils Reimers and Iryna Gurevych, ``Sentence-BERT: Sentence Embeddings using Siamese BERT-Networks'', arXiv:1908.10084, 2019. \url{https://arxiv.org/abs/1908.10084}.

\bibitem{consultantbert}
Dor Lavi, Volodymyr Medentsiy, and David Graus, ``conSultantBERT: Fine-tuned Siamese Sentence-BERT for Matching Jobs and Job Seekers'', arXiv:2109.06501, 2021. \url{https://arxiv.org/abs/2109.06501}.

\bibitem{ibm-siamese-job}
Xiang Li, Niyu Ge, Chunyan Xiao, and Yen-Yu Chen, ``Matching Resumes to Jobs via Deep Siamese Network'', Companion Proceedings of The Web Conference (WWW), 2018. \url{https://research.ibm.com/publications/matching-resumes-to-jobs-via-deep-siamese-network}.

\bibitem{splade}
Thibault Formal, Benjamin Piwowarski, and Stéphane Clinchant, ``SPLADE: Sparse Lexical and Expansion Model for First Stage Ranking'', arXiv:2107.05720, 2021. \url{https://arxiv.org/abs/2107.05720}.

\bibitem{colbertv2}
Keshav Santhanam, Omar Khattab, Jon Saad-Falcon, Christopher Potts, and Matei Zaharia, ``ColBERTv2: Effective and Efficient Retrieval via Lightweight Late Interaction'', NAACL-HLT, 2022. DOI: \url{https://doi.org/10.18653/v1/2022.naacl-main.272}.

\bibitem{hyrr}
Jing Lu, Keith Hall, Ji Ma, and Jianmo Ni, ``HYRR: Hybrid Infused Reranking for Passage Retrieval'', arXiv:2212.10528, 2022. \url{https://arxiv.org/abs/2212.10528}.

\bibitem{lambdamart}
Qiang Wu, Christopher J. C. Burges, Krysta M. Svore, and Jianfeng Gao, ``Adapting Boosting for Information Retrieval Measures'' (LambdaMART), Information Retrieval, 13:254--270, 2010. DOI: \url{https://doi.org/10.1007/s10791-009-9112-1}.

\bibitem{ranklime}
Tanya Chowdhury, Razieh Rahimi, and James Allan, ``Rank-LIME: Local Model-Agnostic Feature Attribution for Learning to Rank'', arXiv:2212.12722, 2022. \url{https://arxiv.org/abs/2212.12722}.

\bibitem{ai-hiring-context}
Sara Kassir, Lewis Baker, Jackson Dolphin, and Frida Polli, ``AI for hiring in context: a perspective on overcoming the unique challenges of employment research to mitigate disparate impact'', AI and Ethics, 3:845--868, 2023. DOI: \url{https://doi.org/10.1007/s43681-022-00208-x}.

\bibitem{ethics-ai-recruiting}
Lisa T. T. Köchling and Marius Wehner, ``Ethics of AI-Enabled Recruiting and Selection: A Review and Research Agenda'', Journal of Business Ethics, 178:977--1007, 2022. DOI: \url{https://doi.org/10.1007/s10551-022-05049-6}.

\end{thebibliography}
